Title Goes Here

### 2021-04-07 analysis/paper/shceof.Rmd
Explica mejor irving2016
(parte de la explicación está en la introducción)
Closes #9

This is analogous to the method of @irving2016, who used reprojection and Fourier filtering to detect "PSA-like" variability and defined as the proper PSA using the peaks of the phase distribution (Compare our Figure\ \@ref(fig:phase-histogram) with their Figure 6).

\textcolor{red}{(Amplia un poco la oración anterior que no queda del todo clara)}

>>>>

This is similar to the method used by @irving2016. From their Fourier decomposition of reprojected meridional wind fields, they show that the phase distribution is bimodal and isolate the PSA pattern from the rest of the PSA-like variability by selecting events that are near the peacks of the distribution (compare our Figure\ \@ref(fig:phase-histogram) with their Figure 6).
